Investigating the Underprovision of Public Goods: Does Segregation Matter?

### 2020-05-09 Burzillo_Trounstine_Replication.Rmd
changes to repo organization
changes to readme

rp <- read_dta("racial_polarization_winners.dta")
fin_seg<- read_dta("fin_seg.dta")

@@

### Figure 7
![This is the original table displaying the results of the models for the effects of residential segregation on political polarization from page 713 of @trounstine_segregation_2016. My replication of these results can be found in Table 5 in the Appendix of this paper.](table_1.png)

>>>>

rp <- read_dta("Trounstine_files/racial_polarization_winners.dta")
fin_seg<- read_dta("Trounstine_files/fin_seg.dta")

@@

### Figure 7
![This is the original table displaying the results of the models for the effects of residential segregation on political polarization from page 713 of @trounstine_segregation_2016. My replication of these results can be found in Table 5 in the Appendix of this paper.](Trounstine_files/table_1.png)
